% Created 2023-10-11 Wed 10:18
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{placeins}
\usepackage{gensymb}
\author{Christian}
\date{\today}
\title{}
\hypersetup{
 pdfauthor={Christian},
 pdftitle={},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.2.50 (Org mode 9.7-pre)}, 
 pdflang={English}}
\begin{document}

\texttt{.Homework}
\section{NAME}
\label{sec:orgad23a84}

Homework - Read and print the contents of files with options.
\section{SYNOPSIS}
\label{sec:orgdc771c4}

\textbf{Homework} [OPTIONS] FILE\ldots{}
\section{DESCRIPTION}
\label{sec:orgd4e71b4}

\textbf{Homework} reads the contents of files and prints them to the standard output line by line. It provides options to control printing behavior.
\section{OPTIONS}
\label{sec:orga94b931}

\begin{itemize}
\item \textbf{\textbf{-h, --help}}: Display this help message.
\item \textbf{\textbf{-r, --reverse}}: Reverse each line before printing.
\item \textbf{\textbf{-d DELAY, --delay DELAY}}: Specify a delay in seconds or fractions thereof. Example: -d 0.5 for a 500 milliseconds delay.
\end{itemize}
\section{FILES}
\label{sec:org0d68a65}

The FILE argument(s) should be the names of the files whose contents need to be printed.
\section{RETURN VALUE}
\label{sec:org938a2a9}

\begin{itemize}
\item 0 on success.
\item 1 on error, such as file not found.
\item All other results printed to STDOUT
\end{itemize}
\section{SEE ALSO}
\label{sec:org37d3416}

\begin{itemize}
\item\relax [man(1)](\url{https://linux.die.net/man/1/man})
\item\relax [getopt(3)](\url{https://linux.die.net/man/3/getopt})
\item\relax [usleep(3)](\url{https://linux.die.net/man/3/usleep})
\item\relax [fprintf(3)](\url{https://linux.die.net/man/3/fprintf})
\end{itemize}
\section{AUTHORS}
\label{sec:orga34be85}

Christian Johnson
\end{document}