% Created 2024-02-01 Thu 11:55
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{placeins}
\usepackage{gensymb}
\author{Christian Johnson}
\date{\today}
\title{UC1 Pickups}
\hypersetup{
 pdfauthor={Christian Johnson},
 pdftitle={UC1 Pickups},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.2.50 (Org mode 9.7-pre)}, 
 pdflang={English}}
\begin{document}

\section*{Pickup Vehicle Use Case}
\label{sec:orgf5264b9}

\subsection*{Scope}
\label{sec:orgd7aced9}
Buoy Rides Automated Rental Pickup
\subsection*{Level}
\label{sec:org91f5af2}
User Goal
\subsection*{Primary Actor}
\label{sec:org57e64c6}
Client
\subsection*{Stakeholders and Interests}
\label{sec:org1973d57}
\begin{itemize}
\item Client: Desires efficient and error-free pickup process to ensure a smooth rental experience.
\item Rental Agent: Aims for seamless vehicle handover to satisfy client needs and company standards.
\item Company: Seeks accurate recording of vehicle pickups to maintain operational integrity and customer satisfaction.
\item Insurance Provider: Interested in capturing insurance purchase decisions for policy management and billing.
\end{itemize}
\subsection*{Preconditions}
\label{sec:org795ed7b}
\begin{enumerate}
\item Client has made a reservation for a vehicle.
\item Client possesses a valid driver's license.
\item Reserved vehicle is available for pickup at the scheduled time.
\end{enumerate}
\subsection*{Success Guarantee (or Postconditions)}
\label{sec:org82df472}
\begin{enumerate}
\item Client successfully collects reserved vehicle.
\item Vehicle's mileage is recorded accurately.
\item Insurance purchase decision, if applicable, is documented.
\item Rental period commences.
\item Vehicle's availability status is updated in the system.
\end{enumerate}
\subsection*{Main Success Scenario (or Basic Flow)}
\label{sec:org715b757}
\begin{enumerate}
\item Client arrives at rental location at scheduled pickup time.
\item Rental agent verifies client's reservation and driver's license.
\item Rental agent hands over keys to reserved vehicle.
\item Rental agent records vehicle's mileage.
\item Rental agent presents insurance options to client.
\item Client decides whether to purchase collision insurance.
\item Rental agent records client's insurance decision.
\item Rental agent provides instructions to client regarding vehicle operation and return.
\item Rental agent updates system to mark vehicle as picked up by client.
\end{enumerate}
\subsection*{Extensions (or Alternative Flows)}
\label{sec:orgf988246}
\begin{itemize}
\item 3a. Reserved vehicle is unavailable; rental agent offers alternative or reschedules pickup.
\item 6a. Client purchases collision insurance; rental agent processes payment and updates agreement.
\item 8a. Issues or concerns arise during pickup; rental agent addresses them accordingly.
\end{itemize}
\end{document}