% Created 2023-10-11 Wed 10:29
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{placeins}
\usepackage{gensymb}
\author{Christian}
\date{\today}
\title{}
\hypersetup{
 pdfauthor={Christian},
 pdftitle={},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.2.50 (Org mode 9.7-pre)}, 
 pdflang={English}}
\begin{document}

\texttt{.Homework}
\section{NAME}
\label{sec:org5f1dc26}

Homework - Read and print the contents of files with options.
\section{SYNOPSIS}
\label{sec:org691cf6e}

\textbf{Homework} [OPTIONS] [FILE\ldots{}]
\section{DESCRIPTION}
\label{sec:orga2b8332}

\textbf{Homework} reads the contents of the specified input file(s) and prints them to STDOUT. Each line can be reversed and a delay can be added between each line. If no files are provided, the program can read from the standard input (stdin).
\section{OPTIONS}
\label{sec:org113dbbf}

\begin{itemize}
\item \textbf{\textbf{-h, --help}}: Display this help message.
\item \textbf{\textbf{-r, --reverse}}: Reverse each line before printing.
\item \textbf{\textbf{-d DELAY, --delay DELAY}}: Specify a delay in seconds or fractions thereof. Example: -d 0.5 for a 500 milliseconds delay.
\end{itemize}
\section{FILE}
\label{sec:org28756a4}

The name(s) of the file(s) to be processed. If no files are provided, the program will read from the standard input (stdin).
\section{RETURN VALUE}
\label{sec:orgf9ec34b}

\begin{itemize}
\item 0 on success.
\item 1 on failure.
\end{itemize}
\section{EXAMPLES}
\label{sec:orga129032}

\begin{itemize}
\item Homework -r -d 0.5 file1.txt file2.txt
Read the contents of file1.txt and file2.txt, reverse each line, and print with a delay of 0.5 seconds between each line.

\item Homework -d 1.0 -r -h
Display the help message.

\item cat file.txt | Homework -r -d 0.5
Read the contents of file.txt from the standard input (stdin), reverse each line, and print with a delay of 0.5 seconds between each line.
\end{itemize}
\section{SEE ALSO}
\label{sec:orgc21d0f7}

\begin{itemize}
\item\relax [man(1)](\url{https://linux.die.net/man/1/man})
\item\relax [cat(1)](\url{https://linux.die.net/man/1/cat})
\item\relax [getopt(3)](\url{https://linux.die.net/man/3/getopt})
\item\relax [usleep(3)](\url{https://linux.die.net/man/3/usleep})
\item\relax [fopen(3)](\url{https://linux.die.net/man/3/fopen})
\end{itemize}
\end{document}